---
title: "My background"
author: "Thais Malta Baracat"
date: '2022-07-25'
output: html_document
---

```{r, echo=FALSE}
knitr::opts_chunk$set(echo=FALSE, error=FALSE, warning=FALSE, message=FALSE)
```

```{r}
#Libraries
library(kableExtra)
library(knitr)
library(tidyverse)
```


# Experience

**ENGIMIND CONSULTORES**  
*Civil Engineer*  
Mar/19 -  Present  
Involved in highways, railways, airports and public and private transportation projects.  

*Engineering Analyst*  
Set/17 - Mar/19  
Involved in highways, railways, ports and public transportation projects.

**UNIVERSITY OF SÃO PAULO**  
*Teaching assistant for R language, FFLCH-USP*  
Mar/21 - Jul/21  
*Introduction of data analysis, programming and visualization for social sciences*, in R language.  

**FCTH**  
*Intern*  
Dec/16 - Aug/17  
Ponta da Madeira Port (Vale, 2017): sedimentation analysis, ship tracking, dredge productivity.  

# Education

**UNIVERSITY OF SÃO PAULO**  
*Master in Transportation planning and operation*  
Feb/19 - Aug/22  
Research: Spatial and temporal analysis of trip patterns from bike-sharing stations.  
Methods: k-means clustering, spatial autocorrelation (Moran's I), multinomial analysis.  

*Bachelor's degree in Civil Engineering*  
Feb/12 - Aug/17  

**ÉCOLE DES PONTS PARISTECH**  
*Eleve stagiaire in Civil Engineering*  
Sep/15 - Jul/16  

# Languages

Portuguese, native speaker  
English, fluent (CPE C2 2018)  
French, advances (DELF B2 2014)  

# Computational skills

Office, QGIS, ArcGIS, AutoCAD, PTV Vissim/Visum, Stata  
Data analysis: VBA and R (Advanced), Python, Matlab, SQL, Tableau, Power BI  

**