---
title: Delay and Cancels - Flights to/from Brazil
author: Thais
date: '2022-08-04'
slug: []
categories:
  - R
tags:
  - R Markdown
  - transportation
---

*By Thais Baracat. August 4, 2022.* <p>

```{r, echo=FALSE}
knitr::opts_chunk$set(echo=FALSE, error=FALSE, warning=FALSE, message=FALSE)
```

```{r}
#Libraries
library(tidyverse)
library(knitr)
library(plotly)
```

#### Introduction

Which companies are the ones who cancels most flights or have most delays in Brazilian flights? Which are the airports with most delays? In order to find out, I have analysed data from the public data provided by *ANAC - Agência Nacional de Aviação Civil*, as detailed below.

#### Data

The data used in this activity is from the 2021 year. The database used containing the following information: company name, flight number, origin and destination airport, number of flights, percentage of flights cancelled, percentage of flights with delays above 30 minutes and percentage of flights with delays above 1 hour. Monthly databases can be found [here].

```{r}
#Abrindo os bancos de dados
atrasos <- read_delim("atrasos.txt", delim = ";")
empresa <- read_delim("empresas.txt", delim = ";", locale = locale(encoding='utf8'))
```

```{r}
#Somando os atrasos mensais por companhia aérea
atrasos_companhia <- atrasos %>% 
  group_by(EMPRESA) %>% 
  summarize(VOOS = sum(VOOS, na.rm = T), 
            CANCELADOS = sum(CANCELADOS, na.rm = T),
            NA_HORA = sum(NA_HORA, na.rm=T),
            ATRASADOS_ACIMA_30 = sum(ATRASADOS_ACIMA_30, na.rm = T),
            ATRASADOS_ACIMA_60 = sum(ATRASADOS_ACIMA_60, na.rm = T))

```

```{r}
#Empresa com mais voos cancelados
cancelados_companhia <- atrasos_companhia %>% 
  mutate(PERC_CANCELADOS = CANCELADOS*100/VOOS) %>%
  dplyr::select(EMPRESA, VOOS, PERC_CANCELADOS)%>% 
  top_n(20,PERC_CANCELADOS) %>% 
  arrange(-PERC_CANCELADOS) %>% 
  left_join(empresa, by=c("EMPRESA")) %>% 
  mutate(AUX_1 = row_number())
```

```{r}
plot_ly(cancelados_companhia
        ,x=~AUX_1
        ,y=~PERC_CANCELADOS
        ,type = 'bar'
        ,text = ~NOME
) %>% 
  layout(xaxis = list(title = 'Airlines with most flights cancelled'), 
         font=t, 
         plot_bgcolor = "#e5ecf6",
         yaxis = list(title = 'Percentage of flights cancelled in 2021'))
```

[here]: https://www.gov.br/anac/pt-br/assuntos/dados-e-estatisticas/percentuais-de-atrasos-e-cancelamentos

